### 2013-06-25 text/paper1/hogg_note.tex
small amount of explanation; new title

\section*{to Adrian from Hogg}

@@

Here's my proposal.
All I have to give you is a likelihood function%
---a probability for the data given parameters---%
and you can take it from there.
Let me know if you want help with priors or sampling.
I don't think this model would be hard to instantiate or sample.
But it \emph{does} have a lot of nuisance parameters (one per star plus some extras).

@@

>>>>

\section*{to APW and KVJ from Hogg}

@@

\paragraph{Here's my proposal:}
All I have to give you is a likelihood function%
---a probability for the data given parameters---%
and you can take it from there.
Let me know if you want help with priors or sampling.
I don't think this model would be hard to instantiate or sample.
But it \emph{does} have a lot of nuisance parameters (one per star plus some extras).

@@

In my way of thinking about it,
the parameters $\omega$, $V$, and all of the $t_i$ are nuisance parameters.
That hurts a bit.
However, the model will work well even with no serious priors on any of these.
The reason is that the Gaussian $N(y\given m,V)$ delivers very high likelihood values
when the data are well explained by small $\det V$.
That's what you want.

~
